---
title: "Building Tidy Data"
author: "Ian Dinwoodie"
date: "`r Sys.Date()`"
output: pdf_document
---

```{r setup, include=FALSE}
library(tidyverse)
knitr::opts_chunk$set(echo=TRUE)
```

# Overview

This notebook serves as reference for the tidying procedures used to prepare the
study data for analysis.

# Building the Data Frame

## Loading the Data Into Memory

We start the tidying process from the manually cleaned data set
(`data/manually-cleaned.csv`) since it is structured and coded appropriately.
Explanations for the various stages of the study data are available in the data
directory README file (`data/README.md`).

```{r}
# TODO: Replace "manually-cleaned-mock.csv" with "manually-cleaned.csv" when it
# is available.
df <- read.csv('../data/manually-cleaned.csv', header=TRUE, skipNul=TRUE)
stopifnot(identical(dim(df)+0, c(2318, 486)))
str(df, list.len=5)
```

## Applying Readable Column Names

Our starting data set is 2318 rows (completed dog entries) by 484 columns (data
fields per dog). A list of improved column names focused on readability has been
provided in the reference directory (`references/readable-column-names.csv`).
Let's load and apply these updated names to our data frame.

```{r}
colnames(df) <- readr::read_lines('../references/readable-column-names.csv')
head(colnames(df), n=5)
```

## Dropping Unnecessary Columns

A list of the necessary columns for tidying the data has been provided in the
reference directory (`references/columns-for-tidying.csv`). Let's load this file
and drop any unmentioned columns.

```{r}
df <- df %>% select(one_of(
  readr::read_lines('../references/columns-for-tidying.csv')))
stopifnot(identical(dim(df)+0, c(2318, 276)))
dim(df)
```

The number of columns is reduced by about 43% and the number of rows remains the
same (as expected).

# Adjusting Data Types

We use the following sections to adjust field types in the data frame.

## Numeric

```{r, warning=FALSE}
df <- df %>%
  mutate_at(vars(matches('_(wks|mos|yrs|dose|freq)$')), funs(as.numeric(.))) %>%
  mutate_at(vars(matches('_time_to_improve$')), funs(as.numeric(.)))
df$weight <- as.numeric(df$weight)

df %>% select(matches('_(wks|mos|yrs)$')) %>% str(list.len=5)
```

## Logical

For some questions where a binary response was desired an additional "I don't
know" response was allowed. We make a first pass through the binary fields to
convert these values to NA. We then make a second pass to convert the fields to
type logical.

```{r}
df <- df %>%
  mutate_at(vars(matches('^(is|has)_')), funs(replace(., . == 2, NA))) %>%
  mutate_at(vars(matches('^(is|has)_')), funs(as.logical(.))) %>%
  mutate(is_male = (sex == 1), .keep = 'unused')
df %>% select(matches('^(is|has)_')) %>% str(list.len=5)
```

## Factor

```{r}
df <- df %>%
  mutate_at(vars(matches('_rating$')), funs(as.factor(.))) %>%
  mutate_at(vars(matches('_units$')), funs(as.factor(.)))
df$purebred_akc_breed <- as.factor(df$purebred_akc_breed)
df$acquisition_source <- as.factor(df$acquisition_source)
df$prof_with_best_results <- as.factor(df$prof_with_best_results)
df$non_improve_ultimate_outcome <- as.factor(df$non_improve_ultimate_outcome)
df$owner_id <- as.factor(df$owner_id)
str(df, list.len=5)
```

# Drop Entires Without Fear/Anxiety

For this study we are investigating fear and anxiety, therefore, we only need to
retain entries relevant to that goal. We use the fear/anxiety binary indicator
to determine which entries should be kept.

```{r}
df <- df %>%
  filter(has_exhibited_fear_anxiety == 1) %>%
  select(-has_exhibited_fear_anxiety)
stopifnot(identical(dim(df)+0, c(1305, 275)))
dim(df)
```

We see that there are entries for 1305 fearful and/or anxious dogs in the data
set and the column count has decremented to 273 as a result of dropping the
fear/anxiety indicator.

# Final Summary

Take a last look at the data before saving it to disk.

```{r}
dim(df)
summary(df)
```

# Saving the Tidy Data

Save the data to a file in the data directory using RDS format so that the data
types are stored and the resulting file is compressed.

```{r}
saveRDS(df, '../data/tidy.Rds')
```
