---
title: "Exploratory Data Analysis (EDA)"
author: "Ian Dinwoodie"
date: "`r Sys.Date()`"
output: html_document
---

```{r setup, include=FALSE}
library(tidyverse)
knitr::opts_chunk$set(echo=TRUE)
```

# Loading the Tidy Data

Load the tidy data from disk.

```{r}
df <- readRDS('../build/tidy.Rds')
stopifnot(identical(dim(df)+0, c(1308, 260)))
str(df, list.len=5)
```

# Descriptive Stats

## Households

Get the nunber of participating dog owners.

```{r}
length(unique(df$owner_id))
```

Determine the median number of dogs per household.

```{r}
summary(as.data.frame(table(df$owner_id))$Freq)
```

## Gender and Neuter Status

```{r}
tbl <- as.numeric(table(df$is_male))
male_cnt <- tbl[2]
female_cnt <- tbl[1]
rm(tbl)

male_prop <- round(male_cnt / (male_cnt + female_cnt) * 100, 2)
print(paste0("Males: ", male_cnt, " (", male_prop, "%)"))
print(paste0("Females: ", female_cnt, " (", 100-male_prop, "%)"))
rm(male_prop)
```

```{r}
tbl <- xtabs(~is_male+is_neutered,data=df)
male_neutered_cnt <- tbl[4]
female_neutered_cnt <- tbl[3]
rm(tbl)

male_neutered_prop <- round(male_neutered_cnt / male_cnt * 100, 2)
print(paste0("Males that are neutered: ", male_neutered_cnt, " (",
             male_neutered_prop, "%)"))
rm(male_cnt, male_neutered_cnt, male_neutered_prop)

female_neutered_prop <- round(female_neutered_cnt / female_cnt * 100, 2)
print(paste0("Females that are neutered: ", female_neutered_cnt, " (",
             female_neutered_prop, "%)"))
rm(female_cnt, female_neutered_cnt, female_neutered_prop)
```

## Ages

```{r}
display_median_with_range <- function(col) {
  col_min <- min(col, na.rm=TRUE)
  col_max <- max(col, na.rm=TRUE)
  col_median <- median(col, na.rm=TRUE)
  col_cnt <- sum(!is.na(col))
  print(paste0("median=", col_median, " (range: ", col_min, " to ", col_max,
               ") (n=", col_cnt, ")"))
}

print("Age at time of study (in months)")
display_median_with_range(df$cur_age_in_mos)
```

```{r}
print("Age at time of acquisition (in months)")
display_median_with_range(df$acq_age_in_mos)
```

```{r}
print("Age at time of neuter (in months)")
display_median_with_range(df$neuter_age_in_mos)
```

## Fear/Anxiety Frequencies

```{r}
cnt <- sum(!is.na(df$inanimate_rating))
total_rows <- dim(df)[1]
proportion <- round(cnt / total_rows * 100, 2)
print(paste0("inanimate=", cnt, " (", proportion, "%)"))
```

```{r}
cnt <- sum(!is.na(df$animate_rating))
proportion <- round(cnt / total_rows * 100, 2)
print(paste0("animate=", cnt, " (", proportion, "%)"))
```

```{r}
cnt <- sum(!is.na(df$situational_rating))
proportion <- round(cnt / total_rows * 100, 2)
print(paste0("situational=", cnt, " (", proportion, "%)"))
```

```{r}
cnt <- sum(!is.na(df$generalized_rating))
proportion <- round(cnt / total_rows * 100, 2)
print(paste0("generalized=", cnt, " (", proportion, "%)"))
```

```{r}
cnt <- sum(!is.na(df$ptsd_rating))
proportion <- round(cnt / total_rows * 100, 2)
print(paste0("ptsd=", cnt, " (", proportion, "%)"))
```

```{r}
cnt <- sum(!is.na(df$fa_overall_rating))
proportion <- round(cnt / total_rows * 100, 2)
print(paste0("fa_overall=", cnt, " (", proportion, "%)"))
```

# Acquisition Source

```{r}
df %>%
  filter(!is.na(acquisition_source)) %>%
  group_by(acquisition_source) %>%
  summarise(n=n()) %>%
  arrange(desc(n))
```

# Purebred Breed

```{r}
df %>%
  filter(!is.na(purebred_breed)) %>%
  group_by(purebred_breed) %>%
  summarise(n=n()) %>%
  arrange(desc(n))
```
# Breakdown of Professionals

```{r}
cnt <- sum(df$has_seen_professional==TRUE, na.rm=TRUE)
proportion <- round(cnt / total_rows * 100, 2)
print(paste0("sought professional help: ", cnt, " (", proportion, ")%"))
```

## Tainers

```{r}
df_t <- df %>%
  filter(has_seen_trainer)
t_rows <- dim(df_t)[1]
proportion <- round(t_rows / total_rows * 100, 2)
print(paste0("sought trainer help: ", t_rows, " (", proportion, ")%"))
```

```{r}
cnt <- sum(df$has_seen_multiple_trainers==TRUE, na.rm=TRUE)
proportion <- round(cnt / t_rows * 100, 2)
print(paste0("sought multiple trainers: ", cnt, " (", proportion, ")%"))
```

```{r}
df_t$trainers_count[df_t$has_seen_trainer] <-
  ifelse(df_t$has_seen_multiple_trainers, df_t$trainers_count, 1)
print("median trainers seen")
display_median_with_range(df_t$trainers_count)
```

```{r}
cred_cnt <- sum(df_t$is_trainer_credentialed==TRUE, na.rm=TRUE)
proportion <- round(cred_cnt / t_rows * 100, 2)
print(paste0("sought cred. trainer: ", cred_cnt, " (", proportion, ")%"))
```

```{r}
cnt <- sum(df_t$is_trainer_cpdt_credentialed==TRUE, na.rm=TRUE)
proportion <- round(cnt / cred_cnt * 100, 2)
print(paste0("sought CPDT trainer: ", cnt, " (", proportion, ")%"))
```


```{r}
rm(df_t, t_rows)
```

## Consultants

```{r}
df_c <- df %>%
  filter(has_seen_consultant)
c_rows <- dim(df_c)[1]
proportion <- round(c_rows / total_rows * 100, 2)
print(paste0("sought consultant help: ", c_rows, " (", proportion, ")%"))
```

```{r}
cnt <- sum(df$has_seen_multiple_consultants==TRUE, na.rm=TRUE)
proportion <- round(cnt / c_rows * 100, 2)
print(paste0("sought multiple consultants: ", cnt, " (", proportion, ")%"))
```

```{r}
df_c$trainers_count[df_c$has_seen_consultant] <-
  ifelse(df_c$has_seen_multiple_consultants, df_c$consultants_count, 1)
print("median consultants seen")
display_median_with_range(df_c$consultants_count)
```

```{r}
cred_cnt <- sum(df_c$is_consultant_credentialed==TRUE, na.rm=TRUE)
proportion <- round(cred_cnt / c_rows * 100, 2)
print(paste0("sought cred. consultant: ", cred_cnt, " (", proportion, ")%"))
```

```{r}
print("Count of consultant credentials")
print(paste0("CBCC-KA: ", sum(df_c$is_consultant_cbcc_ka, na.rm=TRUE)))
print(paste0("other: ",
             sum(df_c$is_consultant_credentialed_other,na.rm=TRUE)))
print(paste0("DACVB: ", sum(df_c$is_consultant_dacvb, na.rm=TRUE)))
print(paste0("CDBC: ", sum(df_c$is_consultant_cdbc, na.rm=TRUE)))
print(paste0("ACAAB/CAAB: ", sum(df_c$is_consultant_acaab, na.rm=TRUE)))
```

```{r}
rm(df_c, c_rows, cred_cnt)
```

## Veterinarians

```{r}
df_v <- df %>%
  filter(has_seen_veterinarian)
v_rows <- dim(df_v)[1]
proportion <- round(v_rows / total_rows * 100, 2)
print(paste0("sought veterinarian help: ", v_rows, " (", proportion, ")%"))
```

```{r}
cnt <- sum(df_v$has_vet_found_related_health_issue==TRUE, na.rm=TRUE)
proportion <- round(cnt / v_rows * 100, 2)
print(paste0("found health issue: ", cnt, " (", proportion, ")%"))
```

```{r}
print("Count of specific discovered health issues")
print(paste0("pain: ", sum(df_v$has_vet_found_pain, na.rm=TRUE)))
print(paste0("other: ", sum(df_v$has_vet_found_other_issue, na.rm=TRUE)))
print(paste0("thyroid issue: ",
             sum(df_v$has_vet_found_thyroid_issue, na.rm=TRUE)))
print(paste0("seizures: ", sum(df_v$has_vet_found_seizures,na.rm=TRUE)))

print(paste0("tumor: ", sum(df_v$has_vet_found_tumor, na.rm=TRUE)))
print(paste0("cognitive dysfunction: ",
             sum(df_v$has_vet_found_cognitive_dysfunction, na.rm=TRUE)))


```

```{r}
rm(df_v, v_rows, cnt, proportion)
```

# Medication

```{r}
df_med <- df[c(254,71:191)]
str(df_med, list.len=5)
```

```{r}
cnt <- sum(df_med$is_medication_used, na.rm=T)
proportion <- round(cnt / total_rows * 100, 2)
print(paste0("used medication: ", cnt, " (", proportion, ")%"))
```

```{r}
summary(df_med[4:16])
```

```{r}
# Convert dose to daily dosage (dose x frequency / weight) for (mg/kg/day).
dosage_cols <- c(31,38,45,52,59,66,73,80,87,94,101,108,115)
for(i in 1:length(dosage_cols)) {
  df_med[dosage_cols[i]] = df_med[dosage_cols[i]] * df_med[dosage_cols[i]+1] /
    df_med$weight_kg
}
summary(df_med[dosage_cols])
```

```{r}
# Output dosage record counts.
for(i in 1:length(dosage_cols)) {
  print(names(df_med[dosage_cols[i]]))
  print(total_rows - sum(is.na(df_med[dosage_cols[i]])))
}
```

# Outcomes

## Improvement

```{r}
i_cnt <- sum(df$fa_overall_rating >= 5, na.rm=T)
proportion <- round(i_cnt / total_rows * 100, 2)
print(paste0("showed improvement = ", i_cnt, " (", proportion, "%)"))

cnt <- sum(df$fa_overall_rating >= 5 & df$fa_overall_rating < 6, na.rm=T)
proportion <- round(cnt / i_cnt * 100, 2)
print(paste0("showed >=25% improvement = ", cnt, " (", proportion, "%)"))

cnt <- sum(df$fa_overall_rating >= 6 & df$fa_overall_rating < 7, na.rm=T)
proportion <- round(cnt / i_cnt * 100, 2)
print(paste0("showed >=25% improvement = ", cnt, " (", proportion, "%)"))

cnt <- sum(df$fa_overall_rating >= 7, na.rm=T)
proportion <- round(cnt / i_cnt * 100, 2)
print(paste0("showed >=75% improvement = ", cnt, " (", proportion, "%)"))
```

## Worsened

```{r}
w_cnt <- sum(df$fa_overall_rating <= 3, na.rm=T)
proportion <- round(w_cnt / total_rows * 100, 2)
print(paste0("worsened = ", w_cnt, " (", proportion, "%)"))

cnt <- sum(df$fa_overall_rating > 2 & df$fa_overall_rating <= 3, na.rm=T)
proportion <- round(cnt / w_cnt * 100, 2)
print(paste0("worsened by >=25% = ", cnt, " (", proportion, "%)"))

cnt <- sum(df$fa_overall_rating > 1 & df$fa_overall_rating <= 2, na.rm=T)
proportion <- round(cnt / w_cnt * 100, 2)
print(paste0("worsened by >=50% = ", cnt, " (", proportion, "%)"))

cnt <- sum(df$fa_overall_rating <= 1, na.rm=T)
proportion <- round(cnt / w_cnt * 100, 2)
print(paste0("worsened by >=75% = ", cnt, " (", proportion, "%)"))
```

## Stayed the Same

```{r}
cnt <- total_rows - i_cnt - w_cnt
proportion <- round(cnt / total_rows * 100, 2)
print(paste0("stayed the same = ", cnt, " (", proportion, "%)"))
```



# Save Session Info

```{r}
sessionInfo()
```
